%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Section: Distinguished Recognition
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Distinguished Research \& Recognized Excellence}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  Slide:
%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[t]{\insertsectionhead}
	\vspace{1ex}

	%% Main Block: Prestigious Awards & Invited Works
	\setbeamercolor{block title example}{fg=white, bg=blue!80!black}
	\begin{exampleblock}{\small \textbf{TOP-TIER HONORS \& AWARDS}}
		\vspace{1ex}
		\small
		\begin{columns}[t, onlytextwidth]
			\begin{column}{0.48\textwidth}
				\textbf{\textcolor{blue!80!black}{Best Transactions Paper (2013)}} \\
				\textit{IEEE Trans. CPMT} \\
				\textbf{Legacy:} Pioneered geometric MOR stopping criteria; now an industry standard.

				\vspace{1.5ex}

				\textbf{\textcolor{blue!80!black}{Invited State-of-the-Art (2021)}} \\
				\textit{IEEE Journal of Microwaves} \\
				\textbf{Impact:} Defined the global R\&D roadmap for next-gen EDA tools.
			\end{column}

			\begin{column}{0.48\textwidth}
				\textbf{\textcolor{blue!80!black}{Best Paper Award (2018)}} \\
				\textit{IEEE SPI, Brest} \\
				Time-domain sensitivity analysis.

				\vspace{1.5ex}

				\textbf{\textcolor{blue!80!black}{Best Paper Award (2011)}} \\
				\textit{IEEE SPI, Naples} \\
				Projection-based MOR stopping criteria.
			\end{column}
		\end{columns}
		\vspace{1ex}
	\end{exampleblock}

	%% Secondary Section: Permanent Literature & Stability Research
	\begin{columns}[t, onlytextwidth]

		% Left Side: Permanent Literature
		\begin{column}{0.48\textwidth}
			\setbeamercolor{block title}{fg=white, bg=green!45!black}
			\begin{block}{\small \textbf{PERMANENT LITERATURE}}
				\vspace{0.5ex}
				\small
				\textbf{\textcolor{blue!80!black}{Handbook Chapter (2020)}} \\
				\textit{"MOR in Microelectronics"} \\
				\textbf{In:} \textit{Handbook on MOR}, De Gruyter. \\
				\textcolor{gray}{Foundational reference for the EDA community.}
			\end{block}
		\end{column}

		% Right Side: Stability Pillars
		\begin{column}{0.48\textwidth}
			\setbeamercolor{block title example}{fg=white, bg=gray!70!black}
			\begin{exampleblock}{\small \textbf{STABILITY BREAKTHROUGHS}}
				\vspace{0.5ex}
				\small
				\textbullet~\textbf{2025:} Stability for active-circuit ROMs.\\
				\textbullet~\textbf{2017:} Non-linear network foundations.\\
				\textcolor{red!80!black}{\textbf{Result:}} Eliminated the "unstable model" industrial bottleneck.
			\end{exampleblock}
		\end{column}

	\end{columns}

	\vfill
	\centering
	\textcolor{gray!50}{\rule{0.6\textwidth}{0.4pt}} \\
	\small \textcolor{darkgray}{Research validated by over 15 years of peer-reviewed excellence.}
\end{frame}

