\section{Research Portfolio -- Scope and Breadth}

%%%%%%%%%%%%%%%%%%%%%%
%%%     NORE       %%%
%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}<0>{NOTES TO PRESENTER:}
	%\note{%
	When presenting these slides, don't read the titles. Instead, say this:

	My research record is built on solving the 'Unsolvable' problems of EDA. Whether it was the Best Transaction Paper Award for model-order estimation or my recent 2025 work on active circuit stability, I have consistently focused on bridging mathematical rigor with the scalability required for billion-gate designs. This track record is the foundation upon which I will build the Siemens EDA Chair at USask.
	\begin{itemize}
		\item Focus on top-tier journals (IEEE Transactions) to demonstrate high-impact research.
		\item Highlight awards and recognitions to establish credibility and excellence.
		\item Emphasize the breadth of research topics to show versatility and comprehensive expertise.
	\end{itemize}
	%}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%
%%%     Slide      %%%
%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[t, fragile, allowframebreaks]{Research Breadth: A Depth \& Comprehensive Portfolio}{\vspace*{0.15cm}\textcolor{red}{\normalsize From Interconnects to Nonlinear Systems - A Holistic Approach to EDA Challenges}}
	\setstretch{1.25}
	{\large $\blacktriangleright$ \bfseries RF Application: Nonlinear \& Periodic Systems:}
	\begin{itemize}
		\item \textbf{\blue{IEEE T-MTT (2021):}} Parameterized PSS analysis though DEIM-based MMT \textbf{(Harmonic Balance)}.
		\item \textbf{\blue{IEEE T-MTT (2018):}} NLTLs via DEIM-Based POD interpolation \textbf{(RF)}.
		\item \textbf{\blue{IEEE T-MTT (2017):}} Efficient NLTL simulation \textbf{(RF)}.
	\end{itemize}

	{\large$\blacktriangleright$ \bfseries Signal \& Power Integrity (SPI):}
	\begin{itemize}
		\item \textbf{\blue{IEEE T-Adv. Packag. (2010):}} $z$-Domain basis functions for system ID \textbf{(Data-Driven Macromodeling)}.
		\item \textbf{\blue{IEEE T-CPMT (2013):}} Massively coupled interconnects \textbf{(SI)}.
	\end{itemize}

	{\large$\blacktriangleright$ \bfseries Parameterized \& Statistical MOR:}
	\begin{itemize}
		\item \textbf{\blue{IEEE T-CPMT (2020):}} MIP algorithm (DC-centric models).
		\item \textbf{\blue{IEEE T-EMC (2020):}} Parameterized MOR (Delayed PEEC).
		\item \textbf{\blue{IEEE T-CPMT (2017):}} Variability analysis (NILT/PMOR).
	\end{itemize}

	{\large$\blacktriangleright$ \bfseries Sensitivity \& Optimization:}
	\begin{itemize}
		\item \textbf{\blue{IEEE T-CPMT (2019):}} Time-domain sensitivity for active networks.
	\end{itemize}
	\vfill

	\begin{flushleft}
		{\color{lightgray}\rule{0.75\textwidth}{0.4pt}}
	\end{flushleft}
	\textit{\textbf{Core Focus: IEEE Transactions on}}
	\begin{itemize}
		\item[\nld] Microwave Telecommunications (MTT),
		\item[\nld] Electromagnetic Compatibility (EMC),
		\item[\nld] Components, Packaging and Manufacturing Technology (CPMT) and Advanced Packaging.
	\end{itemize}
\end{frame}
