\section{Research Portfolio -- Scope and Breadth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Slide: Research Breadth & Depth (Modular Blocks)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[t]{Research Breadth: A Comprehensive EDA Portfolio}
	\lmv{-0.5}
	\begin{columns}[t, onlytextwidth]

		%% LEFT COLUMN
		\begin{column}{0.48\textwidth}
			% Pillar 1
			\setbeamercolor{block title example}{fg=white, bg=blue!80!black}
			\begin{exampleblock}{\small \textbf{RF, Nonlinear \& Periodic Systems}}
				\small
				\begin{itemize}
					\item \textbf{IEEE T-MTT (2021):} PSS via DEIM-MMT \textbf{(HB)}.
					\item \textbf{IEEE T-MTT (2018):} NLTLs via DEIM-POD \textbf{(RF)}.
					\item \textbf{IEEE T-MTT (2017):} High-efficiency NLTL simulation.
				\end{itemize}
			\end{exampleblock}

			\vspace{0.5ex}

			% Pillar 2
			\setbeamercolor{block title example}{fg=white, bg=blue!65!black}
			\begin{exampleblock}{\small \textbf{Signal \& Power Integrity (SI/PI)}}
				\small
				\begin{itemize}
					\item \textbf{IEEE T-Adv. Packag. (2010):} System ID via $z$-Domain Basis Functions.
					\item \textbf{IEEE T-CPMT (2013):} Massively coupled interconnects.
				\end{itemize}
			\end{exampleblock}
		\end{column}

		%% RIGHT COLUMN
		\begin{column}{0.48\textwidth}
			% Pillar 3
			\setbeamercolor{block title example}{fg=white, bg=blue!50!black}
			\begin{exampleblock}{\small \textbf{Parameterized \& Statistical MOR}}
				\small
				\begin{itemize}
					\item \textbf{IEEE T-CPMT (2020):} MIP for DC-centric models.
					\item \textbf{IEEE T-EMC (2020):} PMOR for Delayed PEEC.
					\item \textbf{IEEE T-CPMT (2017):} Variability (NILT/PMOR).
				\end{itemize}
			\end{exampleblock}

			\vspace{2.5ex}

			% Pillar 4
			\setbeamercolor{block title example}{fg=white, bg=gray!70!black}
			\begin{exampleblock}{\small \textbf{Sensitivity \& Optimization}}
				\small
				\begin{itemize}
					\item \textbf{IEEE T-CPMT (2019):} Time-domain sensitivity for active networks.
				\end{itemize}
			\end{exampleblock}
		\end{column}
	\end{columns}

	\vfill
	\begin{mybox}[red]
		\normalsize
		"Bridging the gap between physical electromagnetics and computational efficiency by synthesizing Physics-Aware MOR and Uncertainty Quantification to deliver robust, data-driven solutions for the next generation of RF and High-Speed Systems."
	\end{mybox}

	% %% Footer: Journal Summary
	% \begin{beamercolorbox}[wd=\textwidth, sep=1ex, rounded=true]{block body}
	% 	\small
	% 	\textbf{Primary Publication Venues (IEEE Transactions):} \\
	% 	\textcolor{gray}{Microwave Theory \& Tech. (MTT) $\cdot$ Electromagnetic Compatibility (EMC) $\cdot$ Components, Packaging \& Mfg. Tech. (CPMT)}
	% \end{beamercolorbox}
	\vspace{1ex}
\end{frame}

